---
title: "Examine Pilot Data"
author: "Aaron Erlich"
date: "03/06/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE)

```

## Inter Coder Reliability

I need to get the same 10 which were coded by everyone. As far as I can tell, it appears that only **five** of the coders coded these. I believe Dan used a different system.

```{r}
ROUND <- "full_pilot1"
pacman::p_load(tidyverse, tidyselect, irr, kableExtra, irrNA)

icr <- read_csv("./data_raw/Big Data y Acceso a Info en México_June 18, 2019_07.36.csv",)
fs_ps1 <- readRDS("./data_raw/full_sample_post_p1.rds") %>%
  filter(round == ROUND)

#remove gardage rows
icr2 <- icr %>% slice(-(1:2)) %>%
  filter(!(is.na(RecipientEmail)), Progress==100)

#table(icr)

#deal with person who coded from a differet location (uggh)


icr2 <- mutate(icr, folio_id = ifelse(grepl("'", S1),
                                    trimws(S1),
                                    trimws(str_c("'", S1))))

icr2 <- mutate(icr2, coder_id = str_extract(RecipientEmail, "^[[:alnum:]]+"))


 to_eval <- filter(icr2, folio_id %in% fs_ps1$FOLIO)

#get rid of Dan???

binary_vars <- vars_select(names(to_eval), matches("S6_|S10_"))

to_eval<- to_eval %>% mutate_at(vars(binary_vars),
                                list(~dplyr::recode(., `Sí` = 1, `No` = 0, .default = NA_real_)))

# to_eval <- mutate(icr2, Q14 = factor(Q14, levels = c("Poca o nada", 
#                                                   "Menos de la mitad", 
#                                                   "Aproximadamente la mitad",
#                                                   "La mayoría",
#                                                   "Toda")))

#table(icr$unique_coder)

#output where a second coder is missing ----
number_times_coded <- to_eval %>%
  group_by(folio_id) %>%
  summarise(count = n())


n_coder <- filter(number_times_coded, count > 1)
one_coder <-  filter(number_times_coded, count == 1)
```

These have only bee coded once

```{r}
kable(cat(one_coder$folio_id))
```

```{r, results='asis'}
to_eval <- filter(to_eval, folio_id %in% n_coder$folio_id)
coder_ids <- unique(to_eval$coder_id)

for(i in 1:length(binary_vars)) {
  data_wide <- reshape2::dcast(to_eval,  folio_id ~ coder_id , value.var= binary_vars[i], mean)
  #data_wide <- data_wide %>% select(-folio_id) %>%
  data_wide$rater_var <- apply(data_wide[, coder_ids], 1, var, na.rm = TRUE)
  
 print( sprintf("Binary variable %s", binary_vars[i]))
  
  ratings_out <- data_wide %>%
    filter(rater_var > 0 | is.na(rater_var))

#capture the number of coders, get observations with at least 2. 
#output where there is disagreement only
 output <-  ratings_out %>% kable(., escape = TRUE, digit = 2, )
print(output)

to_stat <- select(data_wide, -folio_id, -rater_var)
print(kable(iccNA(to_stat)$ICCs))

cat("\n\n")


kendallW <- kendallNA(to_stat)
print(sprintf("Kendalls W is: %s", kendallW$`Kendall's W`))
#iprint(kripp.alpha(t(to_stat), method = "nominal"))
cat("\n\n")
}
```

Okay, now let's look at agreement. At least for these c coders, it lokes like, mainly for *Toda* folks are in agreement. For the middle categories, it is challenging. If we condensed the categories it would look better. I won't do more until I figure how who the unique coders are
```{r}

# ratings <- select(data_wide, folio_id, contains("Person")) 
# 
# ratings %>% kable(., escape = TRUE)
# 
# kripp.alpha(t(select(ratings, contains("Person"))), method = "ordinal")

# %>%
#   column_spec(1:5, width = "10em")
```

It's hard to get agreement out of all the coders of the 8, where we have all observations we get 3 thare the same across the board.
```{r}

# agree(select(ratings, contains("@")))
```

This is not a sufficient Kripp alpha, but it is getting there. 
```{r}
# kripp.alpha(t(select(ratings, contains("Person"))), method = "ordinal")

```

