---
title: "Examine Pilot Data"
author: "Aaron Erlich"
date: "03/06/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE)

```

## Inter Coder Reliability

I need to get the same 10 which were coded by everyone. As far as I can tell, it appears that only **two** of the coders coded these. I am not really sure why...I hope it's not a sampling thing. We should double check that...

```{r}
pacman::p_load(tidyverse, irr, kableExtra)
icr <- read_csv("./data_raw/Big Data y Acceso a Info en México_June 3, 2019_13.43.csv")
unique_codes <- read_csv("./data_raw/all_coders_coded.csv")

#remove gardage rows
icr <- icr %>% slice(-(1:5))
                     
#table(icr)

#deal with person who coded from a differet location (uggh)
icr <- icr %>% mutate(unique_coder = 
                        case_when(IPAddress %in% c("134.48.232.19", "174.103.168.235") ~ "Person 1",
                                  IPAddress %in% "174.60.143.107 " ~ "Person 2",
                                  IPAddress %in% "189.146.112.34" ~ "Person 3",
                                  IPAddress %in% "200.56.56.9" ~ "Person 4",
                                  IPAddress %in% "189.210.57.88" ~ "Person 5",
                                  IPAddress %in% "67.71.216.6" ~ "Person 6",
                                  IPAddress %in% "158.143.29.226" ~ "Person 7")) 


#get rid of Dan???
icr2 <- icr %>% filter(Q19 %in% unique_codes$folio_id & unique_coder != "Person 7")

icr2 <- mutate(icr2, Q14 = factor(Q14, levels = c("Poca o nada", 
                                                  "Menos de la mitad", 
                                                  "Aproximadamente la mitad",
                                                  "La mayoría",
                                                  "Toda")))

#table(icr$unique_coder)


data_wide <- reshape2::dcast(icr2,  Q19 ~ unique_coder, value.var="Q14")


```
Okay, now let's look at agreement. At least for these two coders, it doesn't look great... If we condensed the categories it would look better. I won't do more until I figure how who the unique coders are
```{r}
ratings <- select(data_wide, `Person 5`, `Person 6`)

table(ratings) %>% kable(.)

agree(ratings)
```

This is not a sufficient Kripp alpha.
```{r}
kripp.alpha(t(ratings), method="ordinal")

```

